\documentclass[a4paper]{article}
\pagenumbering{gobble}% Remove page numbers (and reset to 1)

% ---------------------------------------------------------------
% Package declaration
% ---------------------------------------------------------------
\usepackage{array}
\usepackage{tabu}
\usepackage{geometry}
\usepackage{numdef} % allow numbers in newcommand name
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{color}

% ---------------------------------------------------------------
% Global variables
% ---------------------------------------------------------------
\def \hMargin {1cm}
\def \vMargin {1cm}
\definecolor{purple}{HTML}{2980b9}

% Personal info
\def \email {minhthai40@gmail.com}
\def \address {403C Apt 120 Dist 2, HCMC 700000}
\def \phone {(+84)975-950-945}
\def \name {Minh Thai Pham}
\def \githubUrl {\link{https://github.com/kantlove}{github.com/kantlove}}
\def \linkedinUrl {\link{https://linkedin.com/in/minhthai}{linkedin.com/in/minhthai}}

% ---------------------------------------------------------------
% Config
% ---------------------------------------------------------------
\geometry{
 left=\hMargin,
 right=\hMargin,
 top=\vMargin,
 bottom=\vMargin,
}
\hypersetup{%
  colorlinks=false,% hyperlinks will be black
  linkbordercolor=purple,% hyperlink borders will be red
  pdfborderstyle={/S/U/W 1}% border style will be underline of width 1pt
}
\setlength{\multicolsep}{6.0pt plus 2.0pt minus 1.5pt} % vertical margin of multicol

% ---------------------------------------------------------------
% Commands
% ---------------------------------------------------------------
\newcommand{\bold}[1]{\textbf{#1}}
\newcommand{\empText}[1]{\fontfamily{put}\selectfont#1} % Palatino font
\newcommand{\fSize}[2]{\fontsize{#1}{#1}\selectfont{#2}}
\num\newcommand{\h1}[1]{\bold{\empText{\Large{#1}}}}
\num\newcommand{\h2}[1]{\noindent\bold{\empText{\fSize{11}{#1}}}}
\num\newcommand{\h3}[1]{\noindent\bold{#1}}
\newcommand{\separator}{\noindent\rule[0.2cm]{\linewidth}{0.1pt}}
\newcommand{\link}[2]{\href{#1}{\textcolor{purple}{#2}}}

\newcommand{\threeCols}[3]{%
% \noindent and @{} is needed to remove automatic indentation
% c=horizontal center, m=vertical center
\noindent
\begin{tabu} to \linewidth {@{} X[m]X[c,m]X[r,m] @{}}
  \bold{#1} & \bold{#2} & \bold{#3} \\
\end{tabu}%
}

\newcommand{\twoCols}[2]{%
\noindent
\begin{tabu} to \linewidth {@{} X[m]X[r,m] @{}}
  \bold{#1} & \bold{#2} \\
\end{tabu}%
}

  
% ---------------------------------------------------------------
% Types
% ---------------------------------------------------------------
\let\tempone\itemize
\let\temptwo\enditemize
\renewenvironment{itemize}{\tempone[leftmargin=0.5cm]\setlength{\itemsep}{0cm}}{\temptwo}
  
% ---------------------------------------------------------------
% Document
% ---------------------------------------------------------------
\begin{document}

% ---------------------------------------------------------------
% Header
% ---------------------------------------------------------------
% Inorder to have right-aligned multiline text, nested table is
% needed
\noindent
\begin{tabu} to \linewidth {@{} X[m]X[2,c,m]X[r,m] @{}}
  \address \newline \phone 
  & 
  \h1{\name} 
  & 
  \begin{tabu}{@{} X[r] @{}} \email \\ \githubUrl \\ \linkedinUrl \end{tabu}
\end{tabu}

% ---------------------------------------------------------------
% Experience
% ---------------------------------------------------------------
\bigskip

\h2{Employment}

\separator

\threeCols{Software Engineer Intern}{KMS Inc.}{May 2015 - Aug 2015}
\\Research \& Development Team
\begin{itemize}
\item Wrote script that automatically setups working environment for the team (using Docker and Vagrant).
\item Ran a web scraper to collect and filter all real-estate market data in the city.
\end{itemize}

\threeCols{Backend Developer}{Chopp Inc.}{Sep 2015 - Oct 2015}
\begin{itemize}
\item Saved time of people by delivering market goods based on customers' orders in the mobile app.
\end{itemize}

\threeCols{iOS Developer}{Connekt}{June 2013 - June 2014}
\begin{itemize}
\item Provide a better way to connect entrepreneurs and developers by creating a matching system.
\item Implemented a card-swiping controls similar to the one of Tinder.
\end{itemize}

\smallskip

% ---------------------------------------------------------------
% Technical skills
% ---------------------------------------------------------------
\h2{Technical Skills}\\
\separator

\vspace{-2.5mm}
\begin{itemize}
\item Languages: Java(proficient), some knowledge in C++, C\#, and HTML
\item Windows, Windows Phone, Networking, Compiler.
\end{itemize}

\smallskip

% ---------------------------------------------------------------
% Education
% ---------------------------------------------------------------
\h2{Education}\\
\separator

\smallskip
\threeCols{B.S Computer Science}{Ho Chi Minh University of Science}{Expected graduation 2016}
\begin{itemize}
\item Cumulative GPA: 3.89
\end{itemize}

\h3{Relevant courses}
\begin{multicols}{3}
\noindent
	\begin{itemize}
	\item Data structures
	\item Algorithms and Complexity
	\item Internetworking Protocol
	\item Mobile Development
	\item Languages and Compiler Design
	\end{itemize}
\end{multicols}

\h3{Course projects}
\begin{itemize}
\item \bold{C compiler}: create a compiler for a simple version of C.
\item \bold{Document search engine}: support query of relevant documents.
\item \bold{SocketEx}: improve socket programming in my homework by exploiting the JavaScript callback syntax (similar to socket.io)
\item \bold{P2P music sharer}: browse, share and play songs from other computers in local network.
\end{itemize}

\smallskip

% ---------------------------------------------------------------
% Project Experience
% ---------------------------------------------------------------
\h2{Project Experience}\\
\separator

\twoCols{BusMap}{Multi-platform}
Windows Phone Development Team
\begin{itemize}
\item Help working people and students travel around the city faster by giving bus directions, bus information, and real-time bus tracking (like Uber).
\item Implement the app for Windows Phone 8.1 platform.
\end{itemize}

\twoCols{TODOs Parser extension}{TypeScript, VS Code}
\begin{itemize}
\item Parses all TODO single/multiline comments in current project.
\item Supports 14 programming languages.
\end{itemize}

\twoCols{JSON Compressor}{Java}
\begin{itemize}
\item Compress Json file up to 50\% and still keep the Json format.
\end{itemize}

\twoCols{GoMusic}{C\#, WP8}
\begin{itemize}
\item Developed a music player app with automatic lyrics searching.
\end{itemize}

\twoCols{Elderly's Pal}{C\#, Kinect}
\begin{itemize}
\item Help elder people track their health and entertain while sitting on their sofas at home.
\end{itemize}

\smallskip

% ---------------------------------------------------------------
% Additional Experience and Awards
% ---------------------------------------------------------------
\h2{Additional Experience and Awards}\\
\separator

\vspace{-2.5mm}
\begin{itemize}
\item Second Prize in Vietnamese Talent Award in Technology, 2015.
\item Qualify for 2nd national round of Microsoft Imagine Cup, 2013.
\end{itemize}

\end{document}